Supplementary Materials- A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-05-19 analysis/paper/supplementary-material.Rmd
edit the SI

## Assessment of MCMC output and Goodness-of-fit diagnostics for our models {.unnumbered}

As an informal way to diagnose model convergence, we first evaluated three diagnostic visual summaries of our MCMC output, including density plots, trace plots, and autocorrelation plots for both models (Figure \@ref(fig:figure-pre-diag) and Figure \@ref(fig:figure-post-diag)) [@Hamra2013]. In general, models with informative priors have a better convergence of the MCMC. We can see that the diagnostic plots show stationary distributions and a trend of decreased autocorrelation. Then we summarize output from our two models by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distributions of the parameters of each model [@Caimo2011; @Caimo2017]. We set $`r bgof_si`$ network graphs simulated from the estimated posterior distribution in ERGMs.

>>>>

## Assessment of priors, MCMC outputs and Goodness-of-fit diagnostics for our models {.unnumbered}

We conducted a sensitivity analysis to understand the effect of the prior specification on our two models. We set all the priors to be vague normal distribution (mean is 0 with standard deviation is 10) and a range of plausible priors (mean from 0 to 5 and standard deviation from 0 to 10). The comparison demonstrates that our results are robust to different priors that preserve the differences between our two models, especially for density, transitivity, and centralization. In general, models with informative priors have a better convergence of the MCMC presented by a trend of decreased autocorrelation for some of the parameters in both models. However, the posterior estimates in 95% confidence intervals could vary for some covariates with different priors.

As an informal way to diagnose model convergence, we evaluated three diagnostic visual summaries of our MCMC output, including density plots, trace plots, and autocorrelation plots for both models (Figure \@ref(fig:figure-pre-diag) and Figure \@ref(fig:figure-post-diag)) [@Hamra2013]. We can see that the diagnostic plots show a trend of stationary distributions for most of the variables. However, the degree of autocorrelation is high at 40 lag for all variable but the dyadcov variable that indicates slow mixing and strong correlations between our samples [@Lynch2007; @Roy2020]. Then we summarize output from our two models by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distributions of the parameters of each model [@Caimo2011; @Caimo2017]. We set $`r bgof_si`$ network graphs simulated from the estimated posterior distribution in ERGMs.
